---
title: "task 10 - 1"
author: "Paulius Kostickis"
date: "Monday, April 18, 2016"
output: html_document
---
1. For this exercise, use the price of a dozen eggs in the United States
from 1900–1993 (data set eggs). Experiment with the various options
in the holt() function to see how much the forecasts change
with damped or exponential trend. Also try changing the parameter
values for  and  to see how they affect the forecasts. Try to
develop an intuition of what each parameter and argument is doing
to the forecasts.
[Hint: use h=100 when calling holt() so you can clearly see the
differences between the various options when plotting the forecasts.]
Which model gives the best RMSE?
Do the residuals from the best model look like white noise?

```{r,include=FALSE}
library(fpp)
library(knitr)

```
y = cumsum(rnorm(300))
plot(y, type="l", main="eksponentinis glodinimas")

alpha = 0.5
l1 = filter(y*alpha, f=1-alpha,method = "recursive")
lines(l1, col=2)


alpha = 0.2
l1 = filter(y*alpha, f=1-alpha,method = "recursive")
lines(l1, col=3)


alpha = 0.1
l1 = filter(y*alpha, f=1-alpha,method = "recursive")
lines(l1, col=4)




```{r}
tsdisplay(eggs, plot.type="scatter")   # matomas trendas ir ciklai
fit=holt(eggs,h=100,exponential=T)
plot(fit)
plot(fit$model)
plot(fit, plot.conf=FALSE)
lines(fitted(fit), col="red")
fit$model

fit2 <- ses(eggs)
plot(fit2$model)
plot(fit2, plot.conf=FALSE)
lines(fit$mean, col="red")


summary(fit)
alpha = 0.5
l1 = filter(eggs*alpha, f=1-alpha,method = "recursive")
lines(l1, col=2)
mod$components
plot(mod)
```