---
title: "task14"
author: "Paulius Kostickis"
date: "Thursday, May 05, 2016"
output: html_document
---

1. For the wmurders data:
(a) if necessary, find a suitable Box-Cox transformation for the data;

```{r,include=F}
library(fpp)
library(knitr)
```

wmurders duomenys - nužudyta moterų iš 100 tūkst., matuota nuo 1950 iki 2004.
Kaip matome nėra didelių svyravimų, todėl nebūtina transformuoti.
```{r}
data=wmurders
tsdisplay(data, plot.type="scatter")  

```

(b) fit a suitable ARIMA model to the transformed data using auto.arima();

Auto.arima taikoma duomenim:
```{r}
auto.arima(data)
```

Gaunama ARIMA(1,2,1)

(c) try some other plausible models by experimenting with the orders chosen;

Reikia iš pradžių duomenis padaryti stacionarius:
```{r}

nd=ndiffs(data)
diffdata <- diff(data,differences=nd)
plot(diffdata)
kpss.test(diffdata)  # p-vaule > 0.05 H0 neatmetame, kad duomenys stacionarūs.
```

Kaip matome iš ACF ir PACF grafikų nieko negalime sužinoti kokį ARIMA modelį naudoti, nes nei vienas nėra gęstančio grafiko ar kelių reikšmingų lag'ų:

```{r}
par(mfrow=c(1,2))
pacf(diffdata)
acf(diffdata)
```

Tai tuomet bandysime automatiškai parinktą modelį truputi keisti:
```{r}
AICc(arima(data,c(1,2,3)))

```

(d) choose what you think is the best model and check the residual
diagnostics;
(e) produce forecasts of your fitted model. Do the forecasts look
reasonable?

(f) compare the results with what you would obtain using ets()
(with no transformation).















2. For the usgdp data:
(a) if necessary, find a suitable Box-Cox transformation for the data;
(b) fit a suitable ARIMA model to the transformed data using
auto.arima();
(c) try some other plausible models by experimenting with the
orders chosen;
(d) choose what you think is the best model and check the residual
diagnostics;
(e) produce forecasts of your fitted model. Do the forecasts look
reasonable?
(f) compare the results with what you would obtain using ets()
(with no transformation).
3. For the mcopper data:
(a) if necessary, find a suitable Box-Cox transformation for the data;
(b) fit a suitable ARIMA model to the transformed data using
auto.arima();
(c) try some other plausible models by experimenting with the
orders chosen;
(d) choose what you think is the best model and check the residual
diagnostics;
(e) produce forecasts of your fitted model. Do the forecasts look
reasonable?
(f) compare the results with what you would obtain using ets()
(with no transformation).