---
title: "Task 7 - 3"
output: html_document
---
```{r,include=F}
library(fpp)
```

3. For the data set bricksq:
(a) Split the data into two parts
```{r}
bricks1 <- window(bricksq, end=1987.99)
bricks2 <- window(bricksq, start=1988)
````
(b) Check that your data have been split appropriately by produc-

ing the following plot.
```{r}
plot(bricksq)
lines(bricks1,col="red")
lines(bricks2,col="blue")
````

(c) Calculate forecasts using each of the four benchmark methods
applied to bricks1.
```{r}
vid=meanf(bricks1, h=20)
naive=rwf(bricks1, h=20) 
snaive=snaive(bricks1, h=20)
drift=rwf(bricks1, drift=TRUE, h=20)
plot(vid)
plot(naive)
plot(snaive)
plot(drift)
```

(d) Compare the accuracy of your forecasts against the actual val-
ues stored in bricks2.
```{r}
accuracy(vid,bricks2)
accuracy(naive,bricks2)
accuracy(snaive,bricks2)
accuracy(drift,bricks2)
```
(e) Which method does best? Why?
Tikrai galime atmesti vidurkio metodą, nes jų paklaidos daug didesnės nei kitų modelių. Manau pagal MPE nereikėtų rinktis modelio, nes šis rodiklis labiau aptinka paslinktumą, nes ne absoliučios reikšmės skaičiuojamos. O kadangi MPE likusių modelių panašios, tai šis rodiklis nieko mums nepasako.

```{r}

```

(f) For the best method, compute the residuals and plot them. For
example
res <- residuals(f1)
plot(res)
hist(res, breaks="FD")
Acf(res)
Do the residuals appear to be uncorrelated and normally dis-
tributed?