---
title: "task 14"
author: "Paulius Kostickis"
date: "Tuesday, May 03, 2016"
output: html_document
---
####1. Choose one of the following seasonal time series: condmilk, hsales, uselec

Pasirinksime condmilk duomenis - kondensuoto pieno gamintojo akcijas.

```{r,include=F}
library(fpp)
library(knitr)

```


####(a) Do the data need transforming? If so, find a suitable transformation.

Matome, jog duomenims nebūtina transformacija, nes vienoda variacija. 

```{r}
lambda = BoxCox.lambda(data)                        #randamas lambda  
  trdata = BoxCox(data,lambda = lambda)               #transformuojami duomenys
data=condmilk
tsdisplay(data, plot.type="scatter")
tsdisplay(trdata, plot.type="scatter")
kpss.test(trdata)
acf(data)
```


####(b) Are the data stationary? If not, find an appropriate differencing, which yields stationary data.

Kadangi duomenys turi sezoniškumą, reikia diferencijuoti, kad gauti stacionarius duomenis

```{r}
nd=nsdiffs(trdata)
nd
nd <- ndiffs(trdiff)     
diffdata <- diff(data,differences=nd)
grafikas(data,T)
```

(c) Identify a couple of ARIMA models that might be useful in describing
the time series. Which of your models is the best according
to their AIC values?
(d) Estimate the parameters of your best model and do diagnostic
testing on the residuals. Do the residuals resemble white noise?
If not, try to find another ARIMA model which fits better.
(e) Forecast the next 24 months of data using your preferred model.
(f) Compare the forecasts obtained using ets().

{}