---
title: "Lab session 1 - exercise 1, task 6"
author: "Paulius Kostickis"
date: "Monday, April 04, 2016"
output: html_document
---

Use the Dow Jones index (data set dowjones) to do the following:
(a) Produce a time plot of the series.
(b) Produce forecasts using the drift method and plot them.
(c) Show that the graphed forecasts are identical to extending the
line drawn between the first and last observations.
(d) Try some of the other benchmark functions to forecast the same
data set. Which do you think is best? Why?

```{r,message=F}

library(fpp)

data=dowjones
plot(data)                                                # a) dalis, išbrėžiami duomenys


x=rwf(data, drift=TRUE, h=30)                             # b) dalis, draft prognozė 
plot(x)
```


```{r,message=F}
plot(x)                                                   # c) dalis, įrodome, kad sujungus pirmą ir
lines(c(0,78),c(data[1],data[78]),lwd= 2, col="BLUE")     #    paskutinį tašką, gauname tokį patį rezultatą


```


d) dalis vidurkio prognozė, prastesnė, nes neatsižvelgia į trendą(tačiau tai gali būti ne trendas, o cyklas). Vidurkis blogiau prognozuotų praeities duomenis
```{r}
y=meanf(data, h=30)                                       
plot(y)                                                   
  

```